Supplemental Information for: Aerodigestive sampling reveals altered microbial exchange between lung, oropharyngeal, and gastric microbiomes in children with impaired swallow function

### 2018-11-25 aspiration/plosone_aspiration_supplement.tex
Small changes, not finished but dinner time

\documentclass{article}

\usepackage[colorlinks=true]{hyperref} % for links and urls
\usepackage{amsmath,amssymb} % for math
\usepackage{color,soul} % for highlighting
\usepackage{booktabs,rotating,multirow} % for nice tables
\usepackage{authblk} % for author affiliations
\usepackage{graphicx} % for figures
\graphicspath{{../figures/}}
\usepackage[numbers]{natbib}
\usepackage[above]{placeins} % for FloatBarrier
\usepackage{amsmath} % for pretty fraction text (heatmap caption)
\usepackage{booktabs} % for multi-line table (reflux correlations)
\usepackage{lineno} % for line numbers
\usepackage{geometry} % for margins and supp fig large pages

% Rename supp figures and tables
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}

% Change margins
 \geometry{
 left=1.25in,
 right=1.25in,
 top=1in,
% tmargin=0.5in,
% bottom=0.5in
 }

 % Double-spaced
\usepackage{setspace}
\onehalfspacing

\begin{document}

%\title{The lung microbiome shifts toward the oropharyngeal microbiome in children with oropharyngeal dysphagia and aspiration}
%\title{The oropharyngeal microbiome shapes lung microbial communities in children with oropharyngeal dysphagia and aspiration}
\title{Supplemental Information for: Aerodigestive sampling reveals altered microbial exchange between lung, oropharyngeal, and gastric microbiomes in children with impaired swallow function}
\author[1,2]{Claire Duvallet}
\author[3]{Kara Larson}
\author[4]{Scott Snapper}
\author[3]{Sonia Iosim}
\author[4]{Ann Lee}
\author[4]{Katherine Freer}
\author[5]{Kara May}
\author[1,2]{Eric Alm}
\author[3,*]{Rachel Rosen}
\affil[1]{Department of Biological Engineering, MIT, Cambridge, Massachusetts}
\affil[2]{Center for Microbiome Informatics and Therapeutics, MIT, Cambridge, Massachusetts}
\affil[3]{Aerodigestive Center, Division of Gastroenterology, Hepatology and Nutrition, Boston Children's Hospital, Boston, Massachusetts}
\affil[4]{Division of Gastroenterology, Hepatology and Nutrition, Boston Children's Hospital, Boston, Massachusetts}
\affil[5]{Division of Pulmonary Medicine, Boston Children's Hospital, Boston, Massachusetts}
\affil[*]{Corresponding author}
\date{}

\maketitle

\section{Supplementary Tables and Figures}

@@

\FloatBarrier
\newpage

\end{document}

>>>>

\section{Supplementary Tables and Figures for Chapter 2}

@@
